How to measure the radial velocity of a star:\\The invariant-spectrum case

### 2022-02-05 paper/main.tex
Updates from Overleaf

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    [HOGG: NEED FIGURE HERE]
    \end{center}
    \caption{HOGG: Something that shows the maximum-likelihood radial-velocity estimates for all epochs, that they saturate the bound.\label{fig:mlrvs}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/binarymask.png}
    \end{center}
    \caption{HOGG: A visualization of part of the binary mask.\label{fig:binarymask}}
  \end{mdframed}
\end{figure}

@@

Empirical templates can be created by interpolating spectra to a common logarithmic wavelength grid and averaging.
Interpolations wwre performed with cubic splines.
With an empirical template in hand, cross-correlation doppler shifts can be estimated, updating the beliefs about the spectra rest frames, and then the templates can be re-made.
This process can be iterated to convergence.
In this process, the initialization matters.
In making the results in this \sectionname, we initialized at the wrong binary-mask results shown in \figref{fig:bccfrvswrong}, not at good radial-velocities, and yet the results are excellent.
That is, we didn't cheat.
We show the empirical-spectrum cross-correlation radial-velocity results in \figref{fig:empiricalrvs}

>>>>

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/full.png}
    \includegraphics[width=\textwidth]{../notebook/mlrvs.png}
    \end{center}
    \caption{HOGG: Something that shows the maximum-likelihood radial-velocity estimates for all epochs, that they saturate the bound.\label{fig:mlrvs}}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/binarymask.png}
    \end{center}
    \caption{HOGG: A visualization of part of the binary mask. HOGG: Comment on the left edge (no windows).\label{fig:binarymask}}
  \end{mdframed}
\end{figure}

@@

Empirical templates can be created by interpolating spectra to a common logarithmic wavelength grid and averaging.
Interpolations wwre performed with cubic splines.
With an empirical template in hand, cross-correlation doppler shifts can be estimated, updating the beliefs about the spectra rest frames, and then the templates can be re-made.
This process can be iterated to convergence.
In this process, the initialization matters.
In making the results in this \sectionname, we initialized at the wrong binary-mask results shown in \figref{fig:bccfrvswrong}, not at good radial-velocities, and yet the results are excellent.
That is, we didn't cheat.
We show the empirical template in \figref{fig:empirical} and we show the
empirical-spectrum cross-correlation radial-velocity results in \figref{fig:empiricalrvs}

\begin{figure}[tp]
  \begin{mdframed}
    \begin{center}
    \includegraphics[width=\textwidth]{../notebook/empirical.png}
    \end{center}
    \caption{HOGG: A visualization of part of the empirical template. HOGG: Comment on the left edge (no windows).\label{fig:empirical}}
  \end{mdframed}
\end{figure}
